---
title: "fdrcontrol"
author: "Dougals Wu"
date: "November 2, 2015"
output: html_document
---

The **fdrcontrol** package tends replace *p.adjust(method='BH') or p.adjust(method='fdr')* for a faster filtering step.

The *FDRcontrol* function takes in a vector of p-values and an alpha value (threshold) for controlling false discovery rate. The algorithm used was described in [here]( https://www.urmc.rochester.edu/biostat/people/faculty/TuSite/FDR_procedure.pdf).

The function return 1 when the datapoint is below the threshold and 0 if it is above the threshold.

```{r warning=F, message=F}
set.seed(0)
library(fdrcontrol)
library(dplyr)

alpha <- 0.01

#simulate data
df <- data.frame(p = sample(1000,100000,replace=T)/100000)
hist(df$p)

df %>% 
    mutate(fdr = FDRcontrol(p,alpha))%>%  #usage of the function FDRcontrol
    mutate(padj = p.adjust(p,method='fdr')) -> df
df %>% 
    filter(fdr==1,padj > alpha) #none of the data point disagree 

```

To compare the speed of computation:

```{r}
library(microbenchmark)
microbenchmark(df %>% mutate(FDR = FDRcontrol(p,0.01)),
            df %>% mutate(padj = p.adjust(p,method='fdr')))
```


```